---
title: "SolarMapping"
author: "Jeremy Toepp"
date: "5/20/2020"
output: html_document
---

```{r setup}
knitr::opts_knit$set(echo = TRUE, root.dir = "/Documents/02 - Personal Projects/01 - Solar Mapping Project")
```

# Solar Mapping Project

This project makes use of Python to transform 959 files that include meteorological data. It then uses R to combine all of those into a dataframe and manipulate it from there. The main objective is to interpolate the solar irradiance data and plot it on a map of the U.S. to identify key areas for solar energy production. Because the file integrity is maintained, it is ensured that further analysis can be done on the meteorological data.

```{r}
# install.packages("reticulate")
library(reticulate)
use_condaenv()
```

## Transform the Data
### Import List of Files
```{python}
# import all needed packages
import csv
import os

# change the directory to where all the .csv files are
os.chdir("D:\\Documents\\02 - Personal Projects\\01 - Solar Mapping Project\\Data\\TMY3")

# use the os module to get a list of all .csv files in the directory
dirs = os.listdir('.')
```

### Transform
```{python}
# change the directory to where all the .csv files are
os.chdir("D:\\Documents\\02 - Personal Projects\\01 - Solar Mapping Project\\Data\\TMY3")

# take lat, lon, and elevation and append as a column, then strip rows 1:3 and save the changes
for file in dirs:
    if (file.endswith('.csv')):
        print (file)
        lineCnt = 0
        newCsvLines = []
        with open(file, 'rt') as csvfile:
            line = csv.reader(csvfile, delimiter=',', quotechar='"')
            for row in line:
                lineCnt = lineCnt + 1
                if lineCnt == 2:
                    lat = row[5]
                    long = row[6]
                    el = row[8].strip()
                if lineCnt >= 4:
                    row.append(lat)
                    row.append(long)
                    row.append(el)
                    newCsvLines.append(row)
        with open('%s' % file, 'w', newline='') as csvfile:
            writer = csv.writer(csvfile)
            for l in newCsvLines:
                writer.writerow(l)
```

Set Up R
```{r}
# set working directory
setwd("/Documents/02 - Personal Projects/01 - Solar Mapping Project")

# specify the packages of interest
packages = c("ggplot2",
             "ggcharts",
             "dplyr",
             "readxl")

# use this function to check if each package is on the local machine
# if a package is installed, it will be loaded
# if any are not, the missing package(s) will be installed and loaded
package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE)
  }
})
```



```{r}
# set the input path
inDir <- "/Documents/02 - Personal Projects/01 - Solar Mapping Project/Data/TMY3"

# get a list of all the files
file_list <- list.files(path=inDir, pattern="*.csv")

# take a look
head(file_list)
```


```{r}
# combine all files in the listed directory into one dataframe
# df = dplyr::bind_rows(file_list, )
```

